Quality Definitions of Qualities

### 2019-12-02 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added notes to preformance quality
updated interoperability and visibility

\newcommand{\notdone}[1]{\textcolor{red}{#1}}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}

@@

\subsection{\notdone{Interoperability} \ad{owner}}

@@

\begin{defn}
Interoperability is the ability of two or more systems or components to exchange
information and to use the information that has been exchanged
\citep{IEEEComputerDictionary1991}.
\end{defn}
\begin{defn}
\label{InteroperabilitySelected}
The degree to which two or more systems, products or components can exchange
information and use the information that has been exchanged
\citep{ISO/IEC25010}.
\end{defn}
\begin{defn}
The ability of a system to coexist and cooperate with other systems.
\citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
The capability to communicate, execute programs, and transfer data among various
functional units in a manner that requires the user to have little or no
knowledge of the unique characteristics of those units
\citep{ISO/IEC/IEEE24765}. \wss{We need to fix the author so that this displays properly}
\end{defn}
\begin{defn}Interoperability is a characteristic of a product or system, whose
interfaces are completely understood, to work with other products or systems,
present or future, in either implementation or access, without any restrictions
\citep{AFUL2019}.
\end{defn}
\begin{defn}
Interoperability is the ability of different information systems, devices and
applications (‘systems’) to access, exchange, integrate and cooperatively use
data in a coordinated manner, within and across organizational, regional and
national boundaries, to provide timely and seamless portability of information
and optimize the health of individuals and populations globally. Health data
exchange architectures, application interfaces and standards enable data to be
accessed and shared appropriately and securely across the complete spectrum of
care, within all applicable settings and with relevant stakeholders, including
by the individual \citep{HIMSS2019}.

@@

@@

Definition \ref{VisibilitySelected} is the only one could be found. It is
rephrased because the original one might refer to binary status - ``visible'' or
``unvisible''.

\wss{Did you also look for transparency?  You should be able to find definitions
  for transparency, especially if you look outside of a software context.  For
  instance, \url{https://www.macmillandictionary.com/dictionary/british/transparent}}

>>>>

\newcommand{\notdone}[1]{\textcolor{red}{#1}}
\newcommand{\done}[1]{\textcolor{black}{#1}}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}
\pmi{Wiegers did not discuss this difference.}
\pmi{Speed - change over time; timing - related to specification: when something should happen in relation to something else - state transitions}

@@

\subsection{\done{Interoperability} \ad{owner}}

@@

\begin{defn}
Interoperability is the ability of two or more systems or components to exchange
information and to use the information that has been exchanged
\citep{IEEEComputerDictionary1991}.
\end{defn}
\begin{defn}
\label{InteroperabilitySelected}
The degree to which two or more systems, products or components can exchange
information and use the information that has been exchanged
\citep{ISO/IEC25010}.
\end{defn}
\begin{defn}
The ability of a system to coexist and cooperate with other systems.
\citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
The capability to communicate, execute programs, and transfer data among various
functional units in a manner that requires the user to have little or no
knowledge of the unique characteristics of those units
\citep{ISO/IEC/IEEE24765}.
\end{defn}
\begin{defn}Interoperability is a characteristic of a product or system, whose
interfaces are completely understood, to work with other products or systems,
present or future, in either implementation or access, without any restrictions
\citep{AFUL2019}.
\end{defn}
\begin{defn}
Interoperability is the ability of different information systems, devices and
applications (‘systems’) to access, exchange, integrate and cooperatively use
data in a coordinated manner, within and across organizational, regional and
national boundaries, to provide timely and seamless portability of information
and optimize the health of individuals and populations globally. Health data
exchange architectures, application interfaces and standards enable data to be
accessed and shared appropriately and securely across the complete spectrum of
care, within all applicable settings and with relevant stakeholders, including
by the individual \citep{HIMSS2019}.

@@

\begin{defn}
Visibility provides transparency into the development process. It is the ability
to see progress at any point and determine the distance to completion of a goal.
Visibility provides status of not only the progress of the project, but the
product itself \citep{GSA2019}.
\end{defn}

\begin{defn}
Business process visibility, also called process visibility, is the ability to
accurately and completely view the processes, transactions and other activities
operating within an enterprise \citep{Rouse2013}.
\end{defn}

\begin{defn}
Process transparency refers to the ability to look inside. The “look inside”
provides an in-depth and clear visibility into the business processes and how
these operate \citep{PRIME2019}.
\end{defn}

@@

Definition \ref{VisibilitySelected} points out that documentation is the way to improve visibility. It is
rephrased because the original one might refer to binary status - ``visible'' or
``unvisible''.
